---
title: "JH - Data Products - W2Q - Leaflet Markdown"
author: "Rafael Carvalheira"
date: "5 de julho de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/Rafael/Documents/GitHub/Coursera-JH-DataProducts/")
```

## What

I will show some of the parks available in my city.

For this I choose the most important close to me.

City park data was retrieved from http://geosampa.prefeitura.sp.gov.br
But i was not able to directly input SHP file, so I just got parks area.

The one State park data was retrieved from it's own site http://www.ambiente.sp.gov.br/parquevillalobos/o-parque-hoje/

Geo location of all was manually retrieved directly from google maps.



#The Data

Best/Biggest parks arround:

Name, Latitude, Longitude, Area (m²), Maintained by

Villa Lobos, -23.545742, -46.720601, 732000

Ibirapuera, -23.587381, -46.657641, 1584000

People's, -23.587982, -46.688759, 116383

Alfredo Volpi, -23.587688, -46.702737, 132111

Burle Marx, -23.632993, -46.721715, 189000



##Assigning data to data.frame for leaflet
```{r pressure, results=FALSE, warning=FALSE}
parks <- data.frame("Name"="Villa Lobos","Lat"=-23.545742,"Lng"=-46.720601,"Area"=732000,"Maintained"="State", stringsAsFactors = FALSE)
parks <- rbind(parks,c("Ibirapuera Park", -23.587381,-46.657641, 1584000, "City"))
parks <- rbind(parks,c("People's Park", -23.587982,-46.688759, 116383, "City"))
parks <- rbind(parks,c("Alfredo Volpi Park", -23.587688,-46.702737, 132111, "City"))
parks <- rbind(parks,c("Burle Marx Park", -23.632993,-46.721715, 189000, "City"))

parks$Lat <- as.numeric(parks$Lat)
parks$Lng <- as.numeric(parks$Lng)
parks$Area <- as.numeric(parks$Area)
parks$Maintained <- as.factor(parks$Maintained)

library(leaflet)
```


#Doing the map

For this map I will use circles.

The size of the circle is proportional to the area of the park.

The color of the circle is accordingly with who maintain it.



```{r, message=FALSE}

factpal <- colorFactor(c("Blue","Red"), parks$Maintained)

parks %>%
    leaflet() %>%
    addTiles() %>%
    addCircles(weight = 2, radius = sqrt(parks$Area), popup = parks$Name, color=~factpal(Maintained)) %>%
    addLegend(labels = c("State", "City"), colors = c("Red","Blue"))

```
