---
title: "JH-Data Products - PA - Final - Brazilian National Soccer Championship 2016"
author: "Rafael Carvalheira"
date: "22 de julho de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(dplyr)
library(tidyr)
```


## Understand the evolution of the Championship

- Analyse the graph understanding each round
- Follow your team's path to sucess or destruction

```{r, echo=FALSE}
    #setwd("GitHub/Coursera-JH-DataProducts/JH-DP-PA-Final/")
    cb16 <- read.csv("campeonatoBrasileiro2016.csv", sep = "," )
    names(cb16) <- gsub("X","",names(cb16))
    cb16N <- cb16 %>% gather(Round, Position, -Times)
    cb16N$Round <- as.numeric(cb16N$Round)

          # get the range for the x and y axis 
      xrange <- range(cb16N$Round) 
      yrange <- range(cb16N$Position) 
      times <- cb16N[cb16N$Round==xrange[2],]
      ntimes <- length(unique(cb16N$Times))

      #Build the plot
      plot(cb16N$Round,cb16N$Position,ylim=c(ntimes,1), type = "n"
           ,xlab = "Round", ylab="Position")
      colors <- rainbow(ntimes) 
      linetype <- c(1:ntimes)
      times <- data.frame(times=times$Times,colors=colors,linetype=linetype, finalPos=times$Position)
      
      # add lines 
      for (i in 1:ntimes) { 
          time <- subset(cb16N, Times == times$times[i]) 
          lines(time$Round, time$Position, type="l", lwd=1.5,
                lty=times$linetype[i]
                , col=times$colors[i]) 
      }
      # add a legend 
      legend("right", legend=times$times[1:ntimes], cex=0.8, col=colors,
             lty=times$linetype, title="Team Positions over Rounds")
```

## Understand your team behavior

- How constant was your Team?

```{r, echo=FALSE}
    #setwd("GitHub/Coursera-JH-DataProducts/JH-DP-PA-Final/")
    cb16 <- read.csv("campeonatoBrasileiro2016.csv", sep = "," )
    names(cb16) <- gsub("X","",names(cb16))
    cb16N <- cb16 %>% gather(Round, Position, -Times)
    cb16N$Round <- as.numeric(cb16N$Round)

          # get the range for the x and y axis 
      xrange <- range(cb16N$Round) 
      yrange <- range(cb16N$Position) 
      times <- cb16N[cb16N$Round==xrange[2],]
      ntimes <- length(unique(cb16N$Times))

      #Build the plot
      plot(cb16N$Round,cb16N$Position,ylim=c(ntimes,1), type = "n"
           ,xlab = "Round", ylab="Position")
      colors <- rainbow(ntimes) 
      linetype <- c(1:ntimes)
      times <- data.frame(times=times$Times,colors=colors,linetype=linetype, finalPos=times$Position)
      
      # add line 

          time <- subset(cb16N, Times == times$times[times$times == "Flamengo"]) 
          lines(time$Round, time$Position, type="l", lwd=1.5,
                lty=times$linetype[times$times == "Flamengo"]
                , col=times$colors[times$times == "Flamengo"]) 

      # add a legend 
      legend("right", legend=times$times[times$times == "Flamengo"], cex=0.8
             , col=times$colors[times$times == "Flamengo"],
             lty=times$linetype[times$times == "Flamengo"], title="Team Positions over Rounds")
```


## Get the final results

- Understand how the competition ended
```{r, echo = TRUE}
head(times[,c("times","finalPos")])
```

## Lead the conversation with data!

- Be the one to know all the answers!

```{r}
    teamName <- "Flamengo"
     firsts <- nrow(cb16N[cb16N$Position==1 & cb16N$Times==teamName,])
     best <- min(cb16N[cb16N$Times==teamName,"Position"])
     worst <- max(cb16N[cb16N$Times==teamName, "Position"])
```
 
* Your team: `r teamName` 
* How many weeks leading the championship? `r firsts` 
* Whats the best position? `r best` 
* Whats the wrost position? `r worst` 